Air pollution and agricultural productivity in a developing country^[I thank Ariel Ortiz-Bobea, Marc Bellemare, and David Sungho Park for comments and suggestions that greatly improved the quality of the paper, as well as conference attendees at the 2023 KER International Conference and the Universi

### 2023-11-03 draft/draft.Rmd
slides

# This includes latex arguments
header-includes:
  - \newcommand{\beginappendix}{   
      \setcounter{table}{0}
      \renewcommand{\thetable}{A\arabic{table}} 
      \setcounter{figure}{0} 
      \renewcommand{\thefigure}{A\arabic{figure}}
    }  # Relabel appendix tables/figures as e.g. A1
  - \usepackage[capposition=top]{floatrow}
  - \usepackage{placeins}   # THis is for /FloatBarrier
  - \usepackage{setspace}
  - \usepackage{dcolumn}
  - \usepackage{booktabs}
  - \usepackage{siunitx}
  - \usepackage{amsmath}
  - \usepackage{enumerate}
  - \usepackage[shortlabels]{enumitem}
  - \usepackage[hang,flushmargin]{footmisc}		# no indents on footnotes
  - \usepackage{makecell}
---

@@

# Table
colnames(plantresultstable) <- c("1991", "2001", "2001", "2011")
rownames(plantresultstable) <- c("Population (log)", "", "Area (log)", "", "Urban pop (prop)", "", "Ag. productivity", "", "Pollution (log PM 2.5)", "",
                                "Sub-sample", "Observations")
kable(
      plantresultstable, caption = "Local characteristics and the construction of coal plants",
      align = "cccc", booktabs = TRUE, linesep = "", escape = FALSE
      ) %>%
  footnote(
           "Note: State fixed effects are included in regressions. Robust standard errors are in parentheses. The outcome in the first column is whether the village is within 30km of a coal plant in 1991. The second column is whether a village in 1991 will have a coal plant in 2001, conditional on not having one in 1991. The last two columns are similarly defined, except using 2001 and 2011 as the years. * p<0.10 ** p<0.05 *** p<0.01",
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE,
           escape = FALSE
           ) %>%
  column_spec(1, width = "3.5cm") %>%
  column_spec(c(2:5),width = "2cm") %>%
  row_spec(11, hline_after = TRUE) %>%
  add_header_above(c(" ", "1991 census" = 2, "2001 census" = 2)) %>%
  kable_classic_2()

>>>>

# This includes latex arguments
header-includes:
  - \newcommand{\beginappendix}{   
      \setcounter{table}{0}
      \renewcommand{\thetable}{A\arabic{table}} 
      \setcounter{figure}{0} 
      \renewcommand{\thefigure}{A\arabic{figure}}
    }  # Relabel appendix tables/figures as e.g. A1
  - \usepackage[capposition=top]{floatrow}
  - \usepackage{placeins}   # THis is for /FloatBarrier
  - \usepackage{setspace}
  - \usepackage{dcolumn}
  - \usepackage{booktabs}
  - \usepackage{siunitx}
  - \usepackage{amsmath}
  - \usepackage{enumerate}
  - \usepackage[shortlabels]{enumitem}
  - \usepackage[hang,flushmargin]{footmisc}		# no indents on footnotes
  - \usepackage{makecell}

---

@@

# Table
colnames(plantresultstable) <- c("1991", "2001", "2001", "2011")
rownames(plantresultstable) <- c("Population (log)", "", "Area (log)", "", "Urban pop (prop)", "", "Ag. productivity", "", "Pollution (log PM 2.5)", "",
                                "Sub-sample", "Observations")
kable(    
      plantresultstable, caption = "Local characteristics and the construction of coal plants",
      align = "cccc", booktabs = TRUE, linesep = "", escape = FALSE
      ) %>%
  footnote(
           "Note: State fixed effects are included in regressions. Robust standard errors are in parentheses. The outcome in the first column is whether the village is within 30km of a coal plant in 1991. The second column is whether a village in 1991 will have a coal plant in 2001, conditional on not having one in 1991. The last two columns are similarly defined, except using 2001 and 2011 as the years. * p<0.10 ** p<0.05 *** p<0.01",
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE,
           escape = FALSE
           ) %>%
  column_spec(1, width = "3.5cm") %>%
  column_spec(c(2:5),width = "2cm") %>%
  add_header_above(c(" ", "1991 census" = 2, "2001 census" = 2)) %>%
  kable_classic_2()
